Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-20 main_paper.tex
Move BibTeX database to 'tex' subdirectory
Move bootstraps into 'algorithm' environment
Using an explicit algorithm environment for the bootstrap descriptions
gives us automatic numbering, etc.

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the ``bootstrap data'' the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm 1 describes this procedure step-by-step for clarity.

\textbf{Algorithm 1}: Bootstrap Bias Corrected Point Estimator
 \begin{enumerate}
	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
	\item Estimate local linear regression on both sides of cutoff using bandwidth from step 1 and calculate $\hat{\tau}(h_{n})$.
	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1 and calculate $\tau^{*}$, the difference of two regression functions evaluated at cutoff.
	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 3 on each sides of cutoff.
	\item Apply step 2 on bootstrap data and obtain $\hat{\tau}^{*}$.
	\item Repeat step 4 and 5 for $B$ times and the bias corrected point estimate is given by $\hat{\tau}^{bc}=\hat{\tau} + \tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
 \end{enumerate}

With Algorithm 1 at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$. Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm 1 for every bootstrapped dataset generated, a bootstrap within the bootstrap. Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$. These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.

\textbf{Algorithm 2}: Confidence Interval
 \begin{enumerate}
	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1.
	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
	\item Apply Algorithm 1 (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .
 \end{enumerate}

@@

%%%%%REFERENCES%%%%%%%%%
\clearpage
\bibliographystyle{jpe}
\bibliography{bootrd}
\end{document}

>>>>

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the ``bootstrap data'' the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm~\ref{alg1} describes this procedure step-by-step for clarity.

\begin{algorithm}[Bias correction]\label{alg1}\hfill
 \begin{enumerate}
	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
	\item Estimate local linear regression on both sides of cutoff using bandwidth from step 1 and calculate $\hat{\tau}(h_{n})$.
	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1 and calculate $\tau^{*}$, the difference of two regression functions evaluated at cutoff.
	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 3 on each sides of cutoff.
	\item Apply step 2 on bootstrap data and obtain $\hat{\tau}^{*}$.
	\item Repeat step 4 and 5 for $B$ times and the bias corrected point estimate is given by $\hat{\tau}^{bc}=\hat{\tau} + \tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
 \end{enumerate}
\end{algorithm}

With Algorithm~\ref{alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$. Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm~\ref{alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap. Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$. These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.

\begin{algorithm}[Confidence intervals]\hfill
 \begin{enumerate}
	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1.
	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
	\item Apply Algorithm~\ref{alg1} (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .
 \end{enumerate}
\end{algorithm}

@@

%%%%%REFERENCES%%%%%%%%%
\clearpage
\bibliographystyle{jpe}
\bibliography{tex/references.bib}
\end{document}
